Graph Generators for Data Science: A Survey

### 2018-07-05 generators_analytics.tex
Sherif Changes

Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms. It involves 6 real-world datasets and 2 synthetic datasets generated that cover two commonly used type of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}). The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths. The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} the measures the required time to preprocess and convert the graph into a suitable format for a graph processing system and \emph{Makespan} the measures the total  execution time of a benchmarking workload algorithm. The benchmark also describes experiments for measuring the scalability of the systems under test. To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, \texttt{Granula}\footnote{\url{https://github.com/atlarge-research/granula}}, that consists of three main components: the modeler, the archiver, and the visualizer.

>>>>

\paragraph{Graphalytics} \texttt{Graphalytics}\footnote{\url{http://graphalytics.ewi.tudelft.nl/}} is an industrial-grade benchmark for graph analysis platforms~\cite{Iosup:2016:LGB:3007263.3007270}. It involves 6 real-world datasets and 2 synthetic datasets generated that cover two commonly used type of graphs: social network graphs generated using LDBC SNB graph generator (see Section~\ref{sec:generators_socialnetworks}) and power-law graphs generated by Graph500 (see Section~\ref{sec:generators_general}). The benchmark workload consists of 6 deterministic algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths. The benchmark uses various metrics to measure the performance and throughput for systems under test such as \emph{upload time} the measures the required time to preprocess and convert the graph into a suitable format for a graph processing system and \emph{Makespan} the measures the total  execution time of a benchmarking workload algorithm. The benchmark also describes experiments for measuring the scalability of the systems under test. To facilitate the end user job of running the designed experimental workload, the benchmark provides  a performance evaluation framework, \texttt{Granula}\footnote{\url{https://github.com/atlarge-research/granula}}, that consists of three main components: the modeler, the archiver, and the visualizer.
